Single-step Hybrid Predition

### 2017-02-01 reports/transformed_kernel_predictions.Rmd
Save names of reduced set of 685 hybrids
Init interpretation of predictive abilities

```{r Reduce-Hybrid-Data, dependson="Load-Agro-Data}
pred_df <- pred_df %>%
  filter(Geno %in% red_hybrid)
```

@@

>>>>

```{r Reduce-Hybrid-Data, dependson="Load-Agro-Data"}
red_hybrid <- readRDS("./data/processed/hybrids_685.RDS")
pred_df <- pred_df %>%
  filter(Geno %in% red_hybrid)
```

@@

### Findings

a)   Reduced

   -   For dry matter yield, transcriptomic data clearly perform best.

   -   Genomic do not clearly perform better than pedigree data except for ADF
     and FAT.

   -   Transcripts perform poorly for DMC and STA.

b)   Full

   -   SNP data perform better for all traits compared to pedigree information.

   -   Predictive abilities for the combination of pedigree, SNP and 
     transcriptomic data "ped100-snp77-mrna42" seem to be the result of the
     predictive abilities of the individual predictors weighted by their share
     of the genotypes. 
     For example 
     $$r(\text{ped100-snp77-mrna42}) = r(\text{ped100}) * (1 - 0.77) +
     r(\text{snp77}) * (0.77 - 0.42) + r(\text{mrna42}) * 0.42$$

   -   The predictive ability of only two predictors is typically higher than a
     weighted average of the predictive abilities of the consituting
     individual predictors.

   -   Predictive abilities for FAT and the predictor combination
     "ped100-snp77-mrna42" are difficult to explain.
